### 2023-04-26 chapter1/chapter1.tex
Corrected typo

The identification of sets of densely connected nodes in graphs is known as community detection in network analysis. While many community detection algorithms are available, only some are commonly used in the context of orthology inference. One early method that remains popular is building clusters progressively by identifying nodes that form a triangle with at least two other nodes in the cluster~\cite{Tatusov1997, Jensen2007}. Other approaches include the MCL algorithm, which clusters graphs by similating stochastic flow, and connected components or other single-linkage criteria~\cite{Remm2001, Enright2002, Li2003, Emms2015, Train2017, Cosentino2018}. While these methods are robust when clustering hit graphs derived from smaller or more diverse sets of genomes, they are not suitable for the large number of closely related genomes in this work since they require relatively few edges to define a cluster. For example, the MCL algorithm and connected components method assign a node to a cluster as long as it has a single edge, and triangle clustering only requires two edges to two adjacent nodes.

>>>>

The identification of sets of densely connected nodes in graphs is known as community detection in network analysis. While many community detection algorithms are available, only some are commonly used in the context of orthology inference. One early method that remains popular is building clusters progressively by identifying nodes that form a triangle with at least two other nodes in the cluster~\cite{Tatusov1997, Jensen2007}. Other approaches include the MCL algorithm, which clusters graphs by simulating stochastic flow, and connected components or other single-linkage criteria~\cite{Remm2001, Enright2002, Li2003, Emms2015, Train2017, Cosentino2018}. While these methods are robust when clustering hit graphs derived from smaller or more diverse sets of genomes, they are not suitable for the large number of closely related genomes in this work since they require relatively few edges to define a cluster. For example, the MCL algorithm and connected components method assign a node to a cluster as long as it has a single edge, and triangle clustering only requires two edges to two adjacent nodes.
